\textsf{Are frontier models superhuman chemists?}

### 2024-03-19 src/tex/appendix.tex
modernize latex

\subsection{Related work}
Existing benchmarks such as those from \citet{guo2023large}, \cite{sun2023scieval}, \citet{Schulze_Balhorn_2024}, \citet{Cai_2024} fail to comply with most of the requirements stipulated above (see \Cref{tab:existing benchmarks}). 
While these benchmarks could provide useful insights in the short-term, they cannot follow the rapid additions to the \gls{llm} space. 
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, special focus on chemical safety, employment of diverse prompting strategies and specialized notation for molecules and mathematical symbols. 
Moreover, we believe that our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

@@

\begin{figure}
    \centering
    \includegraphics{figures/question_count_barplot_mcq_vs_general.pdf}
    \caption{\textbf{Number of multiple choice questions vs.\ open-ended questions per topic.} The bar plot shows the number of multiple choice questions and general questions per topic.}
    \script{plot_statistics.py}
\end{figure}

>>>>

\subsection{Related work}
Existing benchmarks such as those from \textcite{guo2023large}, \cite{sun2023scieval}, \textcite{Schulze_Balhorn_2024}, \textcite{Cai_2024} fail to comply with most of the requirements stipulated above (see \Cref{tab:existing benchmarks}). 
While these benchmarks could provide useful insights in the short-term, they cannot follow the rapid additions to the \gls{llm} space. 
\chembench aims to correct this through a set of developments: compatibility with BigBench, end-to-end automation, special focus on chemical safety, employment of diverse prompting strategies and specialized notation for molecules and mathematical symbols. 
Moreover, we believe that our robust framework, including the platform \url{chembench.org}, will engage the community in open-source contributions.

@@

\begin{figure}
    \centering
    \includegraphics{figures/question_count_barplot_mcq_vs_general.pdf}
    \caption{\textbf{Number of multiple choice questions vs.\ open-ended questions per topic.} The bar plot shows the number of multiple choice questions and general questions per topic.}
    \label{fig:question_count_barplot_mcq_vs_general}
    \script{plot_statistics.py}
\end{figure}

### 2024-03-19 src/tex/ms.tex
modernize latex

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\citet{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study.

@@

\appendix
\section{Appendix}
\input{appendix.tex}

\bibliography{references}

\end{document}

>>>>

\paragraph{\enquote{Tiny} subset}
It is important to note that for routine evaluations, a smaller subset of the corpus might be more practical.\cite{polo2024tinybenchmarks}
For instance,~\textcite{liang2023holistic} report costs of more than 10,000 USD for \gls{api} calls for a single evaluation on the \gls{helm} benchmark on a model. 
To address this, we also provide a subset (\variable{output/num_tiny_questions.txt} questions) of the corpus that was curated to be a diverse and representative subset of the full corpus (see \Cref{sec:subset-selection} for details on the curation process).
We also used this subset to seed the app we used for the human baseline study.

@@

\printbibliography

\clearpage
\appendix
\section{Appendix}
\input{appendix.tex}

\printbibliography
\end{document}
